Quantum Magic Games

### 2023-07-05 paper/main.tex
paper => proof kochen-specker

\subsection{Contextuality}
\label{sec:context}

>>>>

\subsection{A Proof of The Kochen-Specker Theorem}
\label{sec:context}

The Kochen-Specker theorem~\cite{kochen:1967} demonstrates
the incompatilibty between an interpretation of quantum mechanics
that is both deterministic ---~in the sense that there exists
hidden variables that we do not have access to, and thus
the stochasticity that we observe is merely epistemic~--- and,
at the same time, noncontextual. Noncontextuality means that
the outcomes of a measurement do not depend on the context,
where a context is a set of compatible observables.

Consider the magic square game described above. In a noncontextual
hidden-variable model, we should be able to ascribe pre-determined
outcomes to the nine observables in each cell. That is, for each
observable \(M_{i, j}\) in a cell \((i, j)\), there should be an
assignment \(v(M_{i, j}) = \pm{}1\). However, as seen in
Section~\ref{sec:classic-sol}, this is impossible. Hence, either the
model must be contextual, meaning that the outcomes of the
measurements are influenced by the context in which they are inserted
---~for instance, pick any observable in the \(3 \times 3\) grid shown
in Figure~\ref{fig:quantum} and recall that it commutes with the other
two observables in the row and also in the column; then, the result of
measuring this observable is influenced by whether you are measuring
it in the row or in the column~---, or there cannot exist hidden
variables governing the values assigned to each observable.
